---
title: "Code Challenge: Data Wrangling"
author: "Kamerin Sandlin"
date: "2026-03-05"
output: 
  md_document:
        variant: gfm 
---

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
```


1. Download two .csv files from Canvas called DiversityData.csv and Metadata.csv, and read them into R using relative file paths.
ANSWER: 
```{r}
metadata  <- read.csv("Datasets/Metadata.csv")
diversity <- read.csv("Datasets/DiversityData.csv")
```

2. Join the two dataframes together by the common column ‘Code’. Name the resulting dataframe 'alpha'.
ANSWER:
```{r}
alpha <- left_join(diversity, metadata, by = "Code")
```

3. Calculate Pielou’s evenness index: Pielou’s evenness is an ecological parameter calculated by the Shannon diversity index (column Shannon) divided by the log of the richness column.
ANSWER: 
```{r}
alpha_even <- alpha %>% mutate(Pielou_evenness = shannon / log(richness))
```

4. Using tidyverse language of functions and the pipe, use the summarise function and tell me the mean and standard error evenness grouped by crop over time.
ANSWER:
```{r}
alpha_average <- alpha_even %>%
     group_by(Crop, Time_Point) %>%
     summarise(mean_evenness = mean(`Pielou_evenness`, na.rm = TRUE), count = n(), sd_evenness = sd(`Pielou_evenness`, na.rm = TRUE), se_evenness = sd_evenness / sqrt(count))
```

5. Calculate the difference between the soybean column, the soil column, and the difference between the cotton column and the soil column
ANSWER:
```{r}
alpha_average2 <- alpha_average %>%
  select(Time_Point, Crop, mean_evenness) %>%
  pivot_wider(names_from = Crop, values_from = mean_evenness) %>%
  mutate(
    diff.cotton.even = Soil - Cotton,
    diff.soybean.even = Soil - Soybean)
```

6. Connecting it to plots; Start with the alpha_average2 dataframe and select the columns Time_Point, diff.cotton.even, and diff.soybean.even. Reshape the data by Use the pivot_longer function to transform the data from wide to long format, creating a new column named diff that contains the values from diff.cotton.even and diff.soybean.even. 
ANSWER:
```{r}
alpha_average2 %>% 
  select(Time_Point, diff.cotton.even, diff.soybean.even) %>% 
  pivot_longer(cols = c(diff.cotton.even, diff.soybean.even), names_to = "diff", values_to = "values") %>% 
  ggplot(aes(x = Time_Point, y = values, color = diff)) + geom_line()
```
The select line will parse just the three types of value wanted.
pivot_longer will transform the data from wide to long format.
**NOTE: AI was used by me to figure out what was wrong with my code that was making it not work, AI gave me this specific code and it finally worked. 

7. Commit and push a gfm .md file to GitHub inside a
directory called Coding Challenge 5. Provide me a link to
your github written as a clickable link in your .pdf or .docx
ANSWER:
Pushed to github under the name CodingChallenge5 


